Testing Methodologies for a Multiplayer Game Protocol\\

### 2020-12-03 paper/PaperDraft2.tex

For the goal of developing and testing the game locally on one machine, we will also be able to leverage the fact that it is built to run in the browser on
an interpreted language to run test suites end to end. Firstly, we will investigate an approach similar to Ariyurek et al[2] in order to develop an automated
system to test the application as well as to automatically find problems with it. Secondly, the fact that the application in its unobstructed build state will have
its internal state visible and inspectable from the outside. That is to say, if we were to run multiple client simulations concurrently, we would be able to inspect
the state of the simulation on each one of the said client machines independently. This would allow us to inspect the correctness of the model in real time from the
perspective of each client. Likewise, the fact that we could control each client independently, we will be able to gauge the susceptibility of the simulation to erroneous
or malicious data by willfully introducing it to one client, and checking if the erroneous data was propagated to the other clients.

\section{Background}

As this protocol will work with 3D graphical data, we need to present some prerequisite ideas that the reader may not be
familiar with. Since the purpose of this paper is not to discuss how 3D graphics work, the explanation will be kept brief
as to only build up the necessary intuition.

@@

[5] J.Peusaari, “Distributed Issues in Real-Time Interactive Simulations”, Department of Technology Lappeenranta University of Technology, Finland,
 Available: https://ieeexplore.ieee.org/abstract/document/5361761
\end{document}

>>>>

\subsection{Network Architecture}

In attempting to understand the architecture of a centralized simulation, we must also understand under which cirmucstances such an architecture is desired. For example,
let's assume that we have some data that we would like to share between one or more clients, with a client being a receiver which is interested in some data. At a very high level, such
a data sharing layout can be split into two categories: peer-peer and client-server. Smed et. al[6] describes the different layouts in detail, however, generally a peer-peer architecture
is defined as having two or more clients which have all, or part of some data which is then shared equally each peer(Fig. 1). In this scenario, each client is equal to every other client, and thus,
would have to be fully connected to one another[6]. This type of architecture has its own advantages when it comes to certain types of systems, such as file sharing and lock-step simulations,
however we cannot maintain the type of centralized simulation which is pertinent to our topic.

\begin{figure}[htbp]
\centerline{\includegraphics [width = 9cm, height = 5cm] {NetworkArchitecture.jpg}}
\caption{Example of a peer to peer and client server architecture}
\end{figure}

Another type of network architecture exists which has one server serve multiple clients, client-server(Fig. 1). In this type of architecture, one node is designated as the server,
and all authoritative communication is handled through it before being sent to the clients[6]. As noted in Fig 1, we can see that any number of clients may connect to the server
at any one time, and clients do not have to be fully connected since the server is the authoritative source. The client-server architecture will be the target of our testing methodologies
and framework. Although peer-peer has its own valid use cases, it is not appropriate for a centralized simulation and would likewise necessitate a different approach to testing.

@@

[5] J.Peusaari, “Distributed Issues in Real-Time Interactive Simulations”, Department of Technology Lappeenranta University of Technology, Finland,
 Available: https://ieeexplore.ieee.org/abstract/document/5361761

[6] J. Smed, “Aspects of Networking in Multiplayer Computer Games“, Proceedings of International Conference on Application and Development of Computer Games in the 21st Century, Hong Kong, 2001,
Available: https://www.researchgate.net/publication/269251176\_Aspects\_of\_Networking\_in\_Multiplayer\_Computer\_Games
\end{document}
